%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

    %---------------------------------------------------------

  \cventry
    {Masters-to-PhD Fast-Track Student (Dept. of Anthropology)} % Job title
    {McMaster University} % Organization
    {Hamilton, Canada} % Location
    {2014 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provide undergraduate-level course instruction and assessment (ANTH and BIO).}
        \item {Provide graduate-level training in laboratory techniques and computational analysis.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Graduate Resident} % Job title
    {Lewis \& Ruth Sherman Centre for Digital Scholarship} % Organization
    {Hamilton, Canada} % Location
    {2017 - 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Software development for high-throughput genomic analyses.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Graduate Fellow} % Job title
    {MacData Institute} % Organization
    {Hamilton, Canada} % Location
    {2017 - 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Formation of the new McMaster Digital Pedagogy Working Group.}
        \item {Graduate Colloquium presentation, community building.}
      \end{cvitems}
    }    

%---------------------------------------------------------

  \cventry
    { Research Assistant (McMaster Ancient DNA Centre)} % Job title
    {McMaster University} % Organization
    {Hamilton, Canada} % Location
    {2014,
    2019 - 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Bioinformatic Analysis}
        \item {Manuscript Preparation}
        \item {DNA Extraction, NGS Library Prep, Bacterial Genome Sequencing}
      \end{cvitems}
    }
    
    %---------------------------------------------------------

  \cventry
    {Volunteer (Dept. of Anthropology)} % Job title
    {University of Toronto Mississauga} % Organization
    {Mississauga, Canada} % Location
    {2013 - 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Annotation of genes associated with pigmentation in East Asian populations.}
      \end{cvitems}
    }

    %---------------------------------------------------------

  \cventry
    {Volunteer, Summer Student (Dept. of Surgery)} % Job title
    {University of Alberta} % Organization
    {Edmonton, Canada} % Location
    {2011 - 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Molecular biology assays and cell tissue culture, DNA sequence analysis.}
        \item {Immunodetection of genes involved in skeletal development.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Undergraduate Thesis Student, (Dept. of Anthropology)} % Job title
    {University of Alberta} % Organization
    {Edmonton, Canada} % Location
    {2012 - 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Scanning Electron Microscopy (SEM) of bone.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

\pagebreak